Supplement: Bootstrapping Domain Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-02-09 paper.tex
Made titles consistent

\begin{abstract}
  Successful approaches to program induction require a
  hand-engineered domain-specific language (DSL),
  constraining the space of allowed programs and imparting
  prior knowledge of the domain.
  We contribute a program learning algorithm
  called \system
  that infers a DSL
  and trains a neural network to
  efficiently search for programs in the learned DSL.
  We use our model to build circuits,
  edit strings, do symbolic regression,
  and synthesize functions on lists,
  in each case showing the model
   learns a domain-specific vocabulary for expressing solutions to the problems in the domain.

>>>>

\begin{abstract}
  Successful approaches to program induction require a hand-engineered
  domain-specific language (DSL), constraining the space of allowed
  programs and imparting prior knowledge of the domain.  We contribute
  a program induction algorithm called \system that learns a DSL and
  trains a neural network to efficiently search for programs in the
  learned DSL.  We use our model to build circuits, edit strings, do
  symbolic regression, and synthesize functions on lists, in each case
  showing the model learns a domain-specific vocabulary for expressing
  solutions to the problems in the domain.

### 2018-02-09 supplement.tex
Made titles consistent

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Bootstrapping Domain Specific Languages for Bayesian Program Learning}

@@

\twocolumn[
\icmltitle{Supplement: Bootstrapping Domain Specific Languages for Bayesian Program Learning}

>>>>

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{\textsc{DreamCoder}: Bootstrapping Domain Specific Languages for Neurally-Guided Bayesian Program Learning}

@@

\twocolumn[
\icmltitle{Supplement: Bootstrapping Domain Specific Languages for Neurally-Guided Bayesian Program Learning}
